---
title: ""
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: no
    toc: yes
    toc_float: yes
  pdf_document:
    number_sections: no
    toc: yes
---

# Maturity ogive for the southern hake stock  {.tabset}




```{r, message=FALSE, warning=FALSE, paged.print=FALSE}
# Load pckgs -------------------------------------------------------------------
library(mgcv)
library(INLA)
library(plyr)
library(tidyr)
library(GGally)
library(lattice)
library(ggplot2)
library(cowplot)
library(glmmTMB)
library(INLAutils)
library(gridExtra)

source("HighstatLibV11.R")

# Read data --------------------------------------------------------------------

rm(list=ls())
data <- read.csv("mat_data.csv", header = T, check.names = FALSE, 
                 sep = ";" ,dec = ".", stringsAsFactors = F)
data$year_mat <- as.factor(data$year_mat)
data$sex <- as.factor(data$sex)
data$lab <- as.factor(data$lab)
data$month <- as.factor(data$month)

# Subset females
last=unique(data$year)
data=subset(data,data$sex==2)
head(data)

# NA's in mat

ind=is.na(data$mat)
ind=which(ind==TRUE)
data=data[-ind,]
```




```{r , message=TRUE, warning=FALSE, paged.print=FALSE}

## Values less that 21cm -------------------------------------------------------

aux=subset(data,data$lt<21)[,c(3,5)]
sum(aux$mat)
ind=which(aux$mat==1)
aux[ind,]

data$mat[data$lt < 21 ] <- 0
```
## Exploratory {.tabset}


```{r echo=FALSE, message=TRUE, warning=FALSE, paged.print=FALSE}

# Exploratory plots ------------------------------------------------------------------------

## Number of samples by year/lab -----------------------------------------------
sample_yr <- as.data.frame(table(data$lab,data$year_mat))
names(sample_yr) <- c("lab","year","freq")
levels(sample_yr$lab) <- c('IEO', 'IPMA')

f1=ggplot(sample_yr, aes(x=as.numeric(as.character(year)), y = freq, fill=lab)) + 
   geom_bar(stat="identity",width=.7, position = "dodge") +theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   theme(plot.title = element_text(size=10))+ theme_light() + xlab("Year")+ylab("Frequency")+ scale_fill_manual(values=c("#383838","dodgerblue3"),name = "Lab.") + facet_wrap(~lab)+  theme(legend.position="none")


  #annotate(geom = "text", x = 60, y = 0.5, label =str ,parse = TRUE)

f1

ggsave("Exploratory - number of samples by lab and year.png", dpi=300, height=4, width=6)

```


## Motivation {.tabset}

```{r}
df2 <- data
mod.lab2 <- glm(mat ~ lt*lab, family = binomial(logit), data = df2) 
summary(mod.lab2)

#L50 Females IEO
-(coef(mod.lab2)[1]/coef(mod.lab2)[2])
#L50 Females IPMA
-(coef(mod.lab2)[1]+coef(mod.lab2)[3])/(coef(mod.lab2)[2]+coef(mod.lab2)[4])
```

```{r, message=FALSE, warning=FALSE}
new.data <- expand.grid(lt= c(0:max(df2$lt)), 
                        lab = c(levels(df2$lab)))
preds <- predict(mod.lab2, newdata = new.data, type = 'link',se.fit = TRUE)
new.data$pred.full1 <- preds$fit
new.data$ymin1 <- new.data$pred.full1 - 1.96*preds$se.fit 
new.data$ymax1 <- new.data$pred.full1 + 1.96*preds$se.fit

new.data$pred.full <-mod.lab2$family$linkinv(new.data$pred.full1)
new.data$ymin <- mod.lab2$family$linkinv(new.data$ymin1)
new.data$ymax <- mod.lab2$family$linkinv(new.data$ymax1)


ind=which(new.data$lab=="ieo")
ind1=which(new.data$lab=="ipma")
vec=c(rep("8.c",length(ind)), rep("9.a",length(ind1)))
new.data$division=as.factor(vec)

ind=which(df2$lab=="ieo")
ind1=which(df2$lab=="ipma")
df2$lab[ind]="8.c"
df2$lab[ind1]="9.a"

#str="L50[27.8.c]= 43.6,L50[27.9.a]= 41.7"
g2 <- ggplot(new.data,aes(x = lt, y = pred.full, col=division)) +
 # facet_wrap(~lab) 
   xlim(0, 115) + 
  geom_ribbon(data = new.data,aes(y = pred.full, ymin = ymin, ymax = ymax),alpha = 0.25) +
  geom_line(data = new.data,aes(y = pred.full)) + ggtitle ("") + theme(plot.title = element_text(size=10))+labs(x = "Length (cm)", y="Maturity") + theme_light() + scale_color_manual(values=c("#383838","dodgerblue3"),name = "Area", labels = c("8c", "9a")) 

  #annotate(geom = "text", x = 60, y = 0.5, label =str ,parse = TRUE)
g2
ggsave("GLM results area specific maturity ogives.png", dpi=300, height=4, width=6)
```


```{r, message=FALSE, warning=FALSE, paged.print=TRUE}
# Prepare data -----------------------------------------------------------------


# Data cut manual: 
NLbins<-c(seq(from=20, to=40, by=1),seq(from=41, to=70, by=1)) 
l_b=length(NLbins)

len=data$lt
l_len=length(len);aux=rep(0,l_len)
for(i in 1:(l_b-1)){
   for(j in 1:l_len){
      if(!is.na(len[j])){
   if(NLbins[i]<=len[j] & len[j]<NLbins[i+1]){
      aux[j]=NLbins[i]
   }} else {aux[j]=NA}
         
         }
}

dat_aux=cbind(len,aux)
data_cut=data
data_cut$lt_cut=aux
data_cut=subset(data_cut,data_cut$lt_cut!=0)
data<-data_cut
years<-as.numeric(as.character(unique(data$year_mat)))


# Response ----------------------------------------------------------------------

data_ieo=subset(data,data$lab=="ieo")
data_ipma=subset(data,data$lab=="ipma")
data=rbind(data_ieo,data_ipma)

ind_ieo=which(data$lab=="ieo")
ind_ipma=which(data$lab=="ipma")
len=length(data$lab)

len_ieo=length(ind_ieo)
len_ipma=length(ind_ipma)

YCombined <- matrix(NA, nrow = len, ncol = 2)
YCombined[1:len_ieo, 1]     <- (data$mat[ind_ieo])
YCombined[(len_ieo+1):(len_ipma+len_ieo), 2] <- (data$mat[ind_ipma])


```

## Model 3 total fix effect length and random effect year  {.tabset}



### Code

```{r, message=FALSE, warning=FALSE, paged.print=TRUE}
# Model 1 ----------------------------------------------------------------------

f3 <-  YCombined ~ 1 + lt +  
                             f(year_mat, model = "iid")

I3 <- inla(f3,
           control.compute = list(config=TRUE,
                                  dic = TRUE, 
                                  cpo=TRUE,
                                  waic=TRUE),
           family = c("binomial","binomial"),
           data = data, 
           control.inla = list(strategy = 'adaptive'), 
           verbose=TRUE, num.threads = 1)

summary(I3)
I3$waic$waic

#INLAutils::plot_fixed_marginals(I3)
#INLAutils::plot_hyper_marginals(I3)
#INLAutils::plot_random_effects(I3)

# Prediction IPS ---------------------------------------------------------------


r=I3
r.samples = inla.posterior.sample(5000, r)
psam <- sapply(r.samples, function(x) {
   
   lt_effect <- x$latent %>% rownames(.) %>% stringr::str_detect("^lt") %>% x$latent[.,]
   intercept <- x$latent %>% rownames(.) %>% stringr::str_detect("^\\(Intercept\\)") %>% x$latent[.,]
   year_effect <- rnorm(length(lt_effect), sd = 1/sqrt(x$hyperpar[1]))
   predictor <- intercept + year_effect + lt_effect*NLbins[-length(NLbins)]
   exp(predictor)/(1 + exp(predictor))
})
q.sam_al_a <- apply(psam, 1, quantile,
                    c(.025, 0.05, 0.5, 0.95, .975), na.rm =TRUE)

```

### Plot

```{r, message=FALSE, warning=FALSE, paged.print=TRUE}
# Plot -------------------------------------------------------------------------

# Year iid
library(ggplot2)
suabinm <- I3$summary.random$year_mat$mean
suabin2 <- I3$summary.random$year_mat$`0.025quant`
suabin9 <-I3$summary.random$year_mat$`0.975quant`
suabinID<-I3$summary.random$year_mat$ID
suabin<-data.frame(suabinm, suabin2,suabin9,suabinID)

p1<-ggplot(data = suabin, aes(x = as.numeric(as.character(suabinID)), y = suabinm, group=1))+
   geom_line(aes(x =as.numeric(as.character(suabinID)), y = suabinm), color="#383838", size=0.9)+ 
   geom_ribbon(aes(x = as.numeric(as.character(suabinID)), ymin = (suabin2), ymax = (suabin9)), 
               alpha = 0.25, fill="gray70", linetype=1)+
   ggtitle(" ")+
   xlab("Year")+
   ylab("Year effect ")+
   ggtitle("") +
   theme_light() 
p1
ggsave("Model 3 total fix effect length and random effect year_year effect.png", dpi=300, height=4, width=5)
# Ogive
df_plot <- data.frame(t(q.sam_al_a))
rownames(df_plot) <- 1:(length(NLbins)-1)
df_plot <- cbind(df_plot, 
                 lt = NLbins[-length(NLbins)])

p2<-ggplot(df_plot) +
   geom_line(aes(x = lt, y = X50.,group=1), color="#383838", size=0.8) +
   geom_ribbon(aes(x = lt, ymin = (X2.5.), ymax = (X97.5.)), 
               alpha = 0.25, fill="gray70", linetype=1)+
#   geom_line(aes(x = lt, (X2.5.)), color = "grey50", size = 0.1, linetype="dashed") + 
#   geom_line(aes(x = lt, (X97.5.)), color = "grey50", size = 0.1, linetype="dashed") +
   xlab("Length (cm)") + ylab("Prob. Maturity") +
   theme_light() + xlim(10,80) + ggtitle("")
  #geom_vline(xintercept=42.01015, 
  #              color = "red", size=0.5)+
  # geom_hline(yintercept=0.5, 
  #    color = "red", size=0.5)

p2
ggsave("Model 3 total fix effect length and random effect year_ogive.png", dpi=300, height=4, width=5)
```


### $L_{50}$ values

Length at 50% maturity.

```{r  ,message=FALSE, warning=FALSE}
# L50 values -------------------------------------------------------------------
L50_calculation=function(psam,NLbins,epsilon){

len=dim(psam)[2]
dat_aux=data.frame(matrix(0,ncol=2,nrow=length(NLbins)-1))
colnames(dat_aux)=c("Lengths","pi")
dat=dat_aux[1,]
for (i in 1:len){
  vector=psam[,i]
  dat_aux$Lengths=NLbins[-length(NLbins)]
  dat_aux$pi=vector
  dat=rbind(dat,dat_aux)
  
}
dat=dat[-1,]
ind=which(dat$pi>=0.5-epsilon & dat$pi<=0.5+epsilon)
lengths=(dat$Lengths[ind])
return(lengths)
}

# Using the new function


lengths=L50_calculation(psam,NLbins,epsilon=0.05)
median(lengths)
quantile(lengths,0.975)
quantile(lengths,0.025)

```


## Model 1 factor year and fix effect length {.tabset}



### Code

```{r ,message=FALSE, warning=FALSE, paged.print=TRUE}
# Model 2 ----------------------------------------------------------------------

f3 <-  YCombined ~ 1 + lt +  year_mat

I3 <- inla(f3,
           control.compute = list(config=TRUE,
                                  dic = TRUE, 
                                  cpo=TRUE,
                                  waic=TRUE),
           family = c("binomial","binomial"),
           data = data, 
           control.inla = list(strategy = 'adaptive'), 
           verbose=TRUE, num.threads = 1)
summary(I3)
I3$waic$waic
# Prediction IPS ---------------------------------------------------------------

r=I3
r.samples = inla.posterior.sample(5000, r)
psam <- sapply(r.samples, function(x) {
   
   lt_effect <- x$latent %>% rownames(.) %>% stringr::str_detect("^lt") %>% x$latent[.,]
   intercept <- x$latent %>% rownames(.) %>% stringr::str_detect("^\\(Intercept\\)") %>% x$latent[.,]
   beta_y <- x$latent %>% rownames(. ) %>% stringr::str_detect("^year_mat") %>% x$latent[.,]
   
   
   
   predictor1990 <- intercept + lt_effect*NLbins[-length(NLbins)]
   
   pre=list();l=length(beta_y)
   for (i in 1:l){
      pre[[i]]=intercept + beta_y[i] + lt_effect*NLbins[-length(NLbins)]
   }
   
   predictor=predictor1990
   
   for (i in 1:l){
      predictor <- c(predictor, pre[[i]])
   }
   
   exp(predictor)/(1 + exp(predictor))
})


q.sam_al_a <- apply(psam, 1, quantile,
                    c(.025, 0.05, 0.5, 0.95, .975), na.rm =TRUE)

```

### Plot

```{r , message=FALSE, warning=FALSE, paged.print=TRUE}
# Plot -------------------------------------------------------------------------
Gyears=unique(data$year_mat)
df_plot <- data.frame(t(q.sam_al_a))
rownames(df_plot) <- 1:((length(NLbins)-1)*length(Gyears))
df_plot <- cbind(df_plot, 
                 year = sort(rep(unique(data$year_mat), (length(NLbins)-1))),
                 lt = (round(rep(NLbins[-length(NLbins)],length(Gyears)))))

f5=ggplot(df_plot) +
   geom_ribbon(aes(x = lt, ymin = (X2.5.), ymax = (X97.5.), group=year), alpha = 0.25, fill="gray70", linetype=1)+
   geom_line(aes(x = lt, y = X50., group = year, col = year)) + scale_color_viridis_d(option="A", alpha=0.7) +xlab("") + ylab("") +
   xlab("Length (cm)") + ylab("Prob. Maturity") +
   ggtitle("") +
   theme_light()+theme(plot.margin = margin(1,1,1.5,1.2, "cm"))+guides(fill = guide_colourbar(barwidth = 0.5, barheight = 10)) +   
  theme(legend.key.size = unit(0.5, 'cm'))   + theme(legend.text = element_text(size=9.5)) +  theme(legend.title = element_text(size=10))+
    labs(col='Year') +  theme(legend.position = "bottom")



f5
ggsave("Model 1 factor year and fix effect length_ogive.png", dpi=300, height=6.5, width=5)
# All years
ggplot(df_plot) +
      geom_line(aes(x = lt, y = X50.,group=1), color="dodgerblue4", size=0.7) +
      geom_ribbon(aes(x = lt, ymin = (X2.5.), ymax = (X97.5.)), 
               alpha = 0.25, fill="gray50", linetype=1)+
      #geom_line(aes(x = lt, (X2.5.)), color = "grey50", size = 0.1, linetype="dashed") + 
      #geom_line(aes(x = lt, (X97.5.)), color = "grey50", size = 0.1, linetype="dashed") +
      xlab("Length (cm)") + ylab("Prob. Maturity") +
      ggtitle("")+
      theme_light() + facet_wrap(~year)




output_ogive_by_year=as.data.frame(cbind(df_plot$lt,df_plot$X50.,df_plot$X2.5.,df_plot$X97.5.))
output_ogive_by_year$year=df_plot$year
colnames(output_ogive_by_year)=c("length","mat","lower","upper","year")

```


### $L_{50}$


```{r , message=FALSE, warning=FALSE, paged.print=TRUE}
L50_calculation_year=function(psam,NLbins,epsilon,Gyears){
  nrow=(length(NLbins)-1)*length(Gyears)
  len=dim(psam)[2]
  year = sort(rep(unique(data$year_mat), (length(NLbins)-1)))
  lt = round(rep(NLbins[-length(NLbins)],length(Gyears)))
        
  dat_aux=data.frame(matrix(0,ncol=3,nrow=nrow))
  colnames(dat_aux)=c("Lengths","pi","year")
  dat=dat_aux[1,]
  for (i in 1:len){
    vector=psam[,i]
    dat_aux$Lengths=lt
    dat_aux$pi=vector
    dat_aux$year=year
    dat=rbind(dat,dat_aux)
    
  }
  dat=dat[-1,]
  
  lengths=list()
  for (i in 1:length(unique(Gyears))){
    dat_y=subset(dat,dat$year==unique(Gyears)[i])
  ind=which(dat_y$pi>=0.5-epsilon & dat_y$pi<=0.5+epsilon)
  
  lengths[[i]]=(dat_y$Lengths[ind])}
  return(lengths)
}



lengths=L50_calculation_year(psam,NLbins,epsilon=0.05,Gyears)

dL50=data.frame(matrix(NA, nrow = length(unique(Gyears)), ncol = 3))
colnames(dL50)=c("L50","lower","upper")
dL50$year=unique(Gyears)
L50_vector=1:length(unique(Gyears))
lower=1:length(unique(Gyears))
upper=1:length(unique(Gyears))

for (i in 1:length(unique(Gyears))){
L50_vector[i]=median(lengths[[i]])
lower[i]=quantile(lengths[[i]],0.025)
upper[i]=quantile(lengths[[i]],0.975)
}

dL50$L50=L50_vector
dL50$lower=lower
dL50$upper=upper

dL50
# Plot L50 ---------------------------------------------------------------------


f6<-ggplot(dL50) +
   geom_line(aes(x = as.numeric(as.character(year)), y = L50,group=1), color="#785A93", size=0.8) +
   geom_ribbon(aes(x = as.numeric(as.character(year)), ymin = (lower), ymax = (upper),group=1), 
               alpha = 0.25, fill="gray70", linetype=1)+
   xlab("Year") + ylab("L50") +
   theme_light() +ggtitle("")


f6

ggsave("Model 1 factor year and fix effect length_L50.png", dpi=300, height=4, width=5)

```




## Model 4 length RW2 and year random effect  {.tabset}



### Code

```{r message=FALSE, warning=FALSE, paged.print=TRUE}
# Model 1 ------------------------------------------------------------------------

f3 <-  YCombined ~ 1 + f(lt_cut,model = "rw2", scale.model = TRUE) +  
                             f(year_mat, model = "iid")

I3 <- inla(f3,
           control.compute = list(config=TRUE,
                                  dic = TRUE, 
                                  cpo=TRUE,
                                  waic=TRUE),
           family = c("binomial","binomial"),
           data = data, 
           control.inla = list(strategy = 'adaptive'), 
           verbose=TRUE, num.threads = 1)

summary(I3)
#INLAutils::plot_fixed_marginals(I3)
#INLAutils::plot_hyper_marginals(I3)
#INLAutils::plot_random_effects(I3)
I3$waic$waic

# Prediction IPS ---------------------------------------------------------------
I1=I3
r=I3
r.samples = inla.posterior.sample(5000, r)
psam <- sapply(r.samples, function(x) {
   
   lt_effect <- x$latent %>% rownames(.) %>% stringr::str_detect("^lt_cut") %>% x$latent[.,]
   intercept <- x$latent %>% rownames(.) %>% stringr::str_detect("^\\(Intercept\\)") %>% x$latent[.,]
   year_effect <- rnorm(length(lt_effect), sd = 1/sqrt(x$hyperpar[2]))
   predictor <- intercept + year_effect + lt_effect
   exp(predictor)/(1 + exp(predictor))
})
q.sam_al_a <- apply(psam, 1, quantile,
                    c(.025, 0.05, 0.5, 0.95, .975), na.rm =TRUE)

```

### Plot

```{r message=FALSE, warning=FALSE, paged.print=TRUE}
# Plot -------------------------------------------------------------------------

# Year iid
library(ggplot2)
suabinm <- I3$summary.random$year_mat$mean
suabin2 <- I3$summary.random$year_mat$`0.025quant`
suabin9 <-I3$summary.random$year_mat$`0.975quant`
suabinID<-I3$summary.random$year_mat$ID
suabin<-data.frame(suabinm, suabin2,suabin9,suabinID)

p1<-ggplot(data = suabin, aes(x = as.numeric(as.character(suabinID)), y = suabinm, group=1))+
   geom_line(aes(x = as.numeric(as.character(suabinID)), y = suabinm), color="#CD5555", size=0.9)+ 
   geom_ribbon(aes(x = as.numeric(as.character(suabinID)), ymin = (suabin2), ymax = (suabin9)), 
               alpha = 0.25, fill="gray70", linetype=1)+
   ggtitle(" ")+
   xlab("Year")+
   ylab("Year effect ")+
   ggtitle("") +
   theme_light() 
p1

ggsave("Model 4 length RW2 and year random effect_year effect.png", dpi=300, height=4, width=5)

# Ogive
df_plot <- data.frame(t(q.sam_al_a))
rownames(df_plot) <- 1:(length(NLbins)-1)
df_plot <- cbind(df_plot, 
                 lt = (round(I3$summary.random$lt_cut$ID)))

p2<-ggplot(df_plot) +
   geom_line(aes(x = lt, y = X50.,group=1), color="#CD5555", size=0.8) +
   geom_ribbon(aes(x = lt, ymin = (X2.5.), ymax = (X97.5.)), 
               alpha = 0.25, fill="gray70", linetype=1)+
#   geom_line(aes(x = lt, (X2.5.)), color = "grey50", size = 0.1, linetype="dashed") + 
#   geom_line(aes(x = lt, (X97.5.)), color = "grey50", size = 0.1, linetype="dashed") +
   xlab("Length (cm)") + ylab("Prob. Maturity") +
   theme_light() + xlim(10,80) + ggtitle("")
  #geom_vline(xintercept=42.01015, 
  #              color = "red", size=0.5)+
  # geom_hline(yintercept=0.5, 
  #    color = "red", size=0.5)

p2

ggsave("Model 4 length RW2 and year random effect_ogive.png", dpi=300, height=4, width=5)

# RW2 length
library(ggplot2)
suabinm <- I3$summary.random$lt_cut$mean
suabin2 <- I3$summary.random$lt_cut$`0.025quant`
suabin9 <-I3$summary.random$lt_cut$`0.975quant`
suabinID<-I3$summary.random$lt_cut$ID
suabin<-data.frame(suabinm, suabin2,suabin9,suabinID)

p1<-ggplot(data = suabin, aes(x = suabinID, y = suabinm, group=1))+
   geom_line(aes(x = suabinID, y = suabinm), color="#CD5555", size=0.9)+ 
   geom_ribbon(aes(x = suabinID, ymin = (suabin2), ymax = (suabin9)), 
               alpha = 0.25, fill="gray70", linetype=1)+
   ggtitle(" ")+
   xlab("Length (cm)")+
   ylab("Length effect ")+
   ggtitle("") +
   theme_light() 
p1

ggsave("Model 4 length RW2 and year random effect_length effect.png", dpi=300, height=4, width=5)

```

### Table

```{r, message=FALSE, warning=FALSE}
# Table ------------------------------------------------------------------------

output_standard_ogive=as.data.frame(cbind(df_plot$lt,df_plot$X50.,df_plot$X2.5.,df_plot$X97.5.))
colnames(output_standard_ogive)=c("length","mat", "lower","upper")
(output_standard_ogive)
```

### L50 values


```{r, message=FALSE, warning=FALSE}
L50_calculation=function(psam,NLbins,epsilon){

len=dim(psam)[2]
dat_aux=data.frame(matrix(0,ncol=2,nrow=length(NLbins)-1))
colnames(dat_aux)=c("Lengths","pi")
dat=dat_aux[1,]
for (i in 1:len){
  vector=psam[,i]
  dat_aux$Lengths=NLbins[-length(NLbins)]
  dat_aux$pi=vector
  dat=rbind(dat,dat_aux)
  
}
dat=dat[-1,]
ind=which(dat$pi>=0.5-epsilon & dat$pi<=0.5+epsilon)
lengths=(dat$Lengths[ind])
return(lengths)
}

# Using the new function


lengths=L50_calculation(psam,NLbins,epsilon=0.05)
median(lengths)
quantile(lengths,0.975)
quantile(lengths,0.025)


```


## Model 2 year fix effect and length RW2 {.tabset}


### Code

```{r message=FALSE, warning=FALSE, paged.print=TRUE}
# Model 2 ------------------------------------------------------------------------------

f3 <-  YCombined ~ 1 + f(lt_cut,model = "rw2", scale.model = TRUE) +  year_mat

I3 <- inla(f3,
           control.compute = list(config=TRUE,
                                  dic = TRUE, 
                                  cpo=TRUE,
                                  waic=TRUE),
           family = c("binomial","binomial"),
           data = data, 
           control.inla = list(strategy = 'adaptive'), 
           verbose=TRUE, num.threads = 1)
summary(I3)

I3$waic$waic

# Prediction IPS ---------------------------------------------------------------

r=I3
r.samples = inla.posterior.sample(5000, r)
psam <- sapply(r.samples, function(x) {
   
   l_effect <- x$latent %>% rownames(.) %>% stringr::str_detect("^lt_cut") %>% x$latent[.,]
   intercept <- x$latent %>% rownames(.) %>% stringr::str_detect("^\\(Intercept\\)") %>% x$latent[.,]
   beta_y <- x$latent %>% rownames(. ) %>% stringr::str_detect("^year_mat") %>% x$latent[.,]
   
   
   
   predictor1990 <- intercept + l_effect 
   
   pre=list();l=length(years)-1
   for (i in 1:l){
      pre[[i]]=intercept + beta_y[i] + l_effect 
   }
   
   predictor=predictor1990
   
   for (i in 1:l){
      predictor <- c(predictor, pre[[i]])
   }
   
   exp(predictor)/(1 + exp(predictor))
})


q.sam_al_a <- apply(psam, 1, quantile,
                    c(.025, 0.05, 0.5, 0.95, .975), na.rm =TRUE)

```

### Plot

```{r message=FALSE, warning=FALSE, paged.print=TRUE}
# Plot -------------------------------------------------------------------------

df_plot <- data.frame(t(q.sam_al_a))
rownames(df_plot) <- 1:((length(NLbins)-1)*length(years))
df_plot <- cbind(df_plot, 
                 year = as.factor(sort(rep(years, (length(NLbins)-1)))),
                 lt = (round(rep(I3$summary.random$lt_cut$ID,length(years)))))


f5=ggplot(df_plot) +
   geom_ribbon(aes(x = lt, ymin = (X2.5.), ymax = (X97.5.), group=year), alpha = 0.25, fill="gray70", linetype=1)+
   geom_line(aes(x = lt, y = X50., group = year, col = year)) + scale_color_viridis_d(option="E", alpha=0.7) +xlab("") + ylab("") +
   xlab("Length (cm)") + ylab("Prob. Maturity") +
   ggtitle("") +
   theme_light()+theme(plot.margin = margin(1,1,1.5,1.2, "cm"))+guides(fill = guide_colourbar(barwidth = 0.5, barheight = 10))+  
  theme(legend.key.size = unit(0.5, 'cm'))+  theme(legend.text = element_text(size=9.5)) +  theme(legend.title = element_text(size=10))+
    labs(col='Year') +  theme(legend.position = "bottom") 
f5
ggsave("Model 2 year fix effect and length RW2_ogive.png", dpi=300, height=6.5, width=5)

# All years
ggplot(df_plot) +
      geom_line(aes(x = lt, y = X50.,group=1), color="#395E8B", size=0.7) +
      geom_ribbon(aes(x = lt, ymin = (X2.5.), ymax = (X97.5.)), 
               alpha = 0.25, fill="gray50", linetype=1)+
      #geom_line(aes(x = lt, (X2.5.)), color = "grey50", size = 0.1, linetype="dashed") + 
      #geom_line(aes(x = lt, (X97.5.)), color = "grey50", size = 0.1, linetype="dashed") +
      xlab("Length (cm)") + ylab("Prob. Maturity") +
      ggtitle("")+
      theme_light() + facet_wrap(~year)





output_ogive_by_year=as.data.frame(cbind(df_plot$lt,df_plot$X50.,df_plot$X2.5.,df_plot$X97.5.))
output_ogive_by_year$year=df_plot$year
colnames(output_ogive_by_year)=c("length","mat","lower","upper","year")




# RW2 length
library(ggplot2)
suabinm <- I3$summary.random$lt_cut$mean
suabin2 <- I3$summary.random$lt_cut$`0.025quant`
suabin9 <-I3$summary.random$lt_cut$`0.975quant`
suabinID<-I3$summary.random$lt_cut$ID
suabin<-data.frame(suabinm, suabin2,suabin9,suabinID)

p1<-ggplot(data = suabin, aes(x = suabinID, y = suabinm, group=1))+
   geom_line(aes(x = suabinID, y = suabinm), color="#395E8B", size=0.9)+ 
   geom_ribbon(aes(x = suabinID, ymin = (suabin2), ymax = (suabin9)), 
               alpha = 0.25, fill="gray70", linetype=1)+
   ggtitle(" ")+
   xlab("Length(cm)")+
   ylab("Length effect ")+
   ggtitle("") +
   theme_light() 
p1

ggsave("Model 2 year fix effect and length RW2_length effect.png", dpi=300, height=4, width=5)



```

### Table

```{r, message=FALSE, warning=FALSE, paged.print=TRUE}
# Table ------------------------------------------------------------------------

output_ogive_by_year
```


### L50

```{r  message=FALSE, warning=FALSE, paged.print=TRUE}
L50_calculation_year=function(psam,NLbins,epsilon,Gyears){
  nrow=(length(NLbins)-1)*length(Gyears)
  len=dim(psam)[2]
  year = sort(rep(unique(data$year_mat), (length(NLbins)-1)))
  lt = round(rep(NLbins[-length(NLbins)],length(Gyears)))
        
  dat_aux=data.frame(matrix(0,ncol=3,nrow=nrow))
  colnames(dat_aux)=c("Lengths","pi","year")
  dat=dat_aux[1,]
  for (i in 1:len){
    vector=psam[,i]
    dat_aux$Lengths=lt
    dat_aux$pi=vector
    dat_aux$year=year
    dat=rbind(dat,dat_aux)
    
  }
  dat=dat[-1,]
  
  lengths=list()
  for (i in 1:length(unique(Gyears))){
    dat_y=subset(dat,dat$year==unique(Gyears)[i])
  ind=which(dat_y$pi>=0.5-epsilon & dat_y$pi<=0.5+epsilon)
  
  lengths[[i]]=(dat_y$Lengths[ind])}
  return(lengths)
}



lengths=L50_calculation_year(psam,NLbins,epsilon=0.05,Gyears)

dL50=data.frame(matrix(NA, nrow = length(unique(Gyears)), ncol = 3))
colnames(dL50)=c("L50","lower","upper")
dL50$year=unique(Gyears)
L50_vector=1:length(unique(Gyears))
lower=1:length(unique(Gyears))
upper=1:length(unique(Gyears))

for (i in 1:length(unique(Gyears))){
L50_vector[i]=median(lengths[[i]])
lower[i]=quantile(lengths[[i]],0.025)
upper[i]=quantile(lengths[[i]],0.975)
}

dL50$L50=L50_vector
dL50$lower=lower
dL50$upper=upper

dL50$year=as.numeric(as.character(dL50$year))

# Plot L50


f6<-ggplot(dL50) +
   geom_line(aes(x = year, y = L50,group=1), color="#395E8B", size=0.8) +
   geom_ribbon(aes(x = year, ymin = (lower), ymax = (upper)), 
               alpha = 0.25, fill="gray70", linetype=1)+
#   geom_line(aes(x = year, (lower)), color = "grey50", size = 0.1, #linetype="dashed") + 
#   geom_line(aes(x = year, (upper)), color = "grey50", size = 0.1, #linetype="dashed") +
   xlab("Year") + ylab("L50") +
   theme_light() +ggtitle("")


f6

ggsave("Model 2 year fix effect and length RW2_L50.png", dpi=300, height=4, width=5)

```

